\section{分类训练与限时训练}

\subsection{使用说明}

\begin{enumerate}
  \item \textbf{分类训练}：按题型逐项突破，标注难度（★基础 / ★★中档 / ★★★拔高）
  \item \textbf{限时训练}：严格控制时间，模拟考场节奏
  \item 每项训练完成后对照解析，标记错题
\end{enumerate}

\subsection{一、阅读理解专项训练}

\begin{enumerate}
  \item[★]（细节理解）According to the passage, when did the author start learning painting?
  \item[★]（细节理解）What is the main purpose of the community program?
  \item[★]（词义猜测）The word "arduous" in paragraph 2 is closest in meaning to \_\_\_\_\_\_. \\
  A. easy \quad B. difficult \quad C. interesting \quad D. boring
  \item[★★]（推理判断）What can be inferred about the author's attitude toward the new policy?
  \item[★★]（主旨大意）What is the best title for the passage?
  \item[★★]（细节理解）Which of the following is TRUE according to the passage?
  \item[★★]（推理判断）What would the author probably do next?
  \item[★★★]（综合）The passage is mainly developed by \_\_\_\_\_\_. \\
  A. comparing different opinions \\
  B. describing a personal experience \\
  C. presenting research findings \\
  D. listing advantages and disadvantages
\end{enumerate}

\subsection{二、七选五专项训练}

\textbf{Passage 1}：How to Stay Motivated in Online Learning

Online learning offers flexibility, but staying motivated can be a challenge. \textbf{1} \underline{\hspace{3cm}} First, set clear goals for each session. \textbf{2} \underline{\hspace{3cm}} Second, create a dedicated study space. \textbf{3} \underline{\hspace{3cm}} Third, connect with fellow learners. \textbf{4} \underline{\hspace{3cm}} Finally, reward yourself after completing tasks. \textbf{5} \underline{\hspace{3cm}}

\begin{verbatim}
A. This helps you stay focused and track your progress.
B. A study group can provide support and accountability.
C. Here are some strategies to keep you on track.
D. This positive reinforcement builds momentum.
E. A quiet, organized environment signals your brain that it's time to learn.
\end{verbatim}

\textbf{Keys}：1. C \quad 2. A \quad 3. E \quad 4. B \quad 5. D

\subsection{三、完形填空专项训练}

\textbf{Passage 1}：

It was a rainy evening. I was waiting for the bus when I noticed a young boy standing alone at the stop. He looked \textbf{1} , holding a broken umbrella. I walked over and offered to share mine. His face \textbf{2} up immediately. We started talking, and I learned that he was waiting for his mother who was \textbf{3} from work. After a few minutes, a car pulled up and the boy's mother \textbf{4} him. She thanked me warmly. That small \textbf{5} of kindness cost me nothing but meant so much.

\begin{enumerate}
  \item[1.] A. excited \quad B. miserable \quad C. curious \quad D. proud
  \item[2.] A. lit \quad B. turned \quad C. gave \quad D. came
  \item[3.] A. returning \quad B. escaping \quad C. suffering \quad D. learning
  \item[4.] A. called \quad B. waved \quad C. greeted \quad D. collected
  \item[5.] A. act \quad B. sign \quad C. sense \quad D. word
\end{enumerate}

\textbf{Keys}：1. B \quad 2. A \quad 3. A \quad 4. D \quad 5. A

\subsection{四、语法填空专项训练}

\textbf{Passage 1}：

Last summer, I volunteered at \textbf{1} \underline{\hspace{1cm}} local library, \textbf{2} \underline{\hspace{1cm}} I spent most of my childhood. My job was \textbf{3} \underline{\hspace{1cm}} (organize) books and help visitors find what they \textbf{4} \underline{\hspace{1cm}} (look) for. It was \textbf{5} \underline{\hspace{1cm}} (challenge) at first, but I soon got used to it. \textbf{6} \underline{\hspace{1cm}} (work) there taught me patience and responsibility. The best part \textbf{7} \underline{\hspace{1cm}} (be) meeting different people every day. I remember \textbf{8} \underline{\hspace{1cm}} old man who came in every Tuesday to read newspapers. We became good friends. This experience made me realize the importance \textbf{9} \underline{\hspace{1cm}} community service. I plan \textbf{10} \underline{\hspace{1cm}} (continue) volunteering next summer.

\textbf{Keys}：1. a \quad 2. where \quad 3. to organize \quad 4. were looking \quad 5. challenging \quad 6. Working \quad 7. was \quad 8. an \quad 9. of \quad 10. to continue

\subsection{五、短文改错专项训练}

\textbf{Passage 1}：

\medskip

My favorite subject is English. I have been learned it for six years. At first, I found it hard to pronounce words correctly. But with my teacher's help, I made a rapid progress. Now I can reading English books without looking up every word. I also enjoy watch English movies. They help me improve my listen skills. However, I still have trouble with writing. I often make mistakes in grammar. I decide to practice more. My goal is to be able to speak English fluent by the end of this year.

\medskip

\textbf{Keys}：
\begin{enumerate}
  \item learned $\to$ \textbf{learning}（have been doing 现在完成进行时）
  \item ✓
  \item a progress $\to$ \textbf{progress}（不可数名词，去掉 a）
  \item reading $\to$ \textbf{read}（can + 动词原形）
  \item watch $\to$ \textbf{watching}（enjoy doing）
  \item listen $\to$ \textbf{listening}（修饰 skills 用 listening）
  \item decide $\to$ \textbf{decided}（时态一致）
  \item ✓
  \item fluent $\to$ \textbf{fluently}（修饰动词 speak 用副词）
  \item ✓
\end{enumerate}

\subsection{六、限时训练}

\subsubsection{限时训练一（基础巩固，30 分钟）}

\textbf{语法填空 10 题 + 短文改错 10 题}

\begin{enumerate}
  \item[语1] I \underline{\hspace{1cm}} (visit) the museum last weekend with my family.
  \item[语2] The book \underline{\hspace{1cm}} (write) by a famous author is very popular.
  \item[语3] We were late \underline{\hspace{1cm}} the heavy traffic.
  \item[语4] She is the girl \underline{\hspace{1cm}} won the first prize.
  \item[语5] I don't know \underline{\hspace{1cm}} he will come or not.
  \item[语6] It is \underline{\hspace{1cm}} (danger) to swim alone in the river.
  \item[语7] More attention should \underline{\hspace{1cm}} (pay) to your pronunciation.
  \item[语8] He runs \underline{\hspace{1cm}} (fast) than any other student in his class.
  \item[语9] We are looking forward to \underline{\hspace{1cm}} (hear) from you.
  \item[语10] The number of the students \underline{\hspace{1cm}} (be) increasing.
  \item[改1] I have went to Beijing last year.
  \item[改2] She is more taller than her sister.
  \item[改3] He enjoys to play basketball.
  \item[改4] There are many people in the street.
  \item[改5] I don't know what is his name.
  \item[改6] The weather is hot and humid, isn't it?
  \item[改7] She always go to school by bus.
  \item[改8] I am interesting in reading novels.
  \item[改9] Neither you nor he are wrong.
  \item[改10] He told me that he will come.
\end{enumerate}

\textbf{目标}：30 分钟，正确率 85\% 以上

\subsubsection{限时训练二（中档强化，60 分钟）}

\textbf{阅读理解 4 篇 + 七选五 1 篇 + 完形填空 1 篇}

\begin{enumerate}
  \item[阅1] 细节理解题型（4 题）
  \item[阅2] 推理判断题型（4 题）
  \item[阅3] 主旨大意题型（4 题）
  \item[阅4] 综合题型（3 题）
  \item[七选五] 1 篇（5 题）
  \item[完形] 1 篇（15 题）
\end{enumerate}

\textbf{目标}：60 分钟，正确率 75\% 以上

\subsubsection{限时训练三（综合模拟，90 分钟）}

\textbf{完整套题训练}：
\begin{enumerate}
  \item 阅读理解 4 篇（15 题，37.5 分）— 35 分钟
  \item 七选五 1 篇（5 题，12.5 分）— 10 分钟
  \item 完形填空 1 篇（15 题，15 分）— 15 分钟
  \item 语法填空 1 篇（10 题，15 分）— 10 分钟
  \item 短文改错 1 篇（10 题，10 分）— 10 分钟
  \item 书面表达 1 篇（25 分）— 10 分钟（列提纲）
\end{enumerate}

\textbf{目标}：90 分钟，总分 105+/150

\subsection{训练记录表}

\begin{center}
\begin{tabular}{c|c|c|c|c}
\textbf{训练类型} & \textbf{正确题数} & \textbf{总题数} & \textbf{得分率} & \textbf{用时} \\ \toprule
阅读理解专项 & & & & \\
七选五专项 & & & & \\
完形填空专项 & & & & \\
语法填空专项 & & & & \\
短文改错专项 & & & & \\
限时训练一 & & & & \\
限时训练二 & & & & \\
限时训练三 & & & & \\
\bottomrule
\end{tabular}
\end{center}

\textit{每次训练后记录，标注薄弱题型，重点突破。建议每周至少完成 2 次限时训练。}
